Multi-Instance Methods for Partially Supervised Image Segmentation

### 2013-09-23 partial_supervision/paper.tex
feedback from a real expert....

Most algorithms for semantic image segmentation and object-class segmentation
work with strong supervision: a pixel-wise labeling of training images. In this
chapter we investigate a method that works with annotation which is much
easier to obtain: whole image labels.
While we do not reach the accuracy of competing fully supervised approaches,
our efficient, semi-supervised method is potentially able to scale to much
larger datasets, without the need of time-consuming manual annotation on
pixel level.

Recently, several approaches have been proposed for semi-supervised semantic
segmentation.  While these are close to our work, there are several important
distinctions.  We address the task of object-class segmentation which concerns
object categories, while semantic segmentation approaches often focus on
"stuff" categories like "sky" and "road" which are more easily detected using
simple texture features.
In contrast to, for example, \citet{vezhnevets2011weakly}, who build a joint model over all
segmentation decisions, our approach is in
principle applicable to large datasets, the regime where weak annotation is
most useful.

>>>>

Most algorithms for semantic image segmentation and object-class segmentation
work with strong supervision: a pixel-wise labeling of training images. In this
chapter we investigate a method that works with annotation which is much
easier to obtain: whole image labels.
While we do not reach the accuracy of competing fully supervised approaches,
our efficient, weakly supervised method is potentially able to scale to much
larger datasets, without the need of time-consuming manual annotation on
pixel level.

Recently, several approaches have been proposed for weakly supervised semantic
segmentation.  While these are close to our work, there are several important
distinctions.  We address the task of object-class segmentation which concerns
object categories, while semantic segmentation approaches often focus on
"stuff" categories like "sky" and "road" which are more easily detected using
simple texture features.
In contrast to, for example, \citet{vezhnevets2011weakly}, who build a joint model over all
segmentation decisions, our approach is in
principle applicable to large datasets, the regime where weak annotation is
most useful.
